### 2021-06-28 docs/submission/srep/coverletter/letter-tex/covlet.tex
#15 polishes cover letter and hopefully build CITEX

%* The affiliation and contact information of your corresponding author
I have the pleasure of sending you the manuscript entitled "Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities" authored by Miguel Xochicale and Chris Baber from the University of Birmingham to be considered for publication as a research article in your prestigious journal.

%* A brief explanation of why the work is appropriate for Scientific Reports
Our work is appropriate for Scientific Reports due to its alignment to the principles of open science (e.g., reproducibility, transparency, reusability and open accessibility) in the fields of physical, biological, health and engineering sciences.
Similarly, we choose Scientific Reports as venue where potential interest of readers in above mentioned areas along with raising interested and spark collaborations.

>>>>

%* The affiliation and contact information of your corresponding author
I have the pleasure of sending you the manuscript entitled 
"Recurrence Quantification Analysis of Movement Variability in Human-Humanoid Interaction Activities"
authored by Miguel Xochicale and Chris Baber from the University of Birmingham to be considered for publication as a research article in your prestigious journal.

%* A brief explanation of why the work is appropriate for Scientific Reports
Our work is appropriate for Scientific Reports due to its alignment to the principles of open science (e.g., reproducibility, transparency, reusability and open accessibility) in the fields of physical, biological, health and engineering sciences.
Similarly, we choose Scientific Reports as venue for publication of multidisciplinary areas where potential interest of readers may be interested and spark collaborations of our work.
